---
title: "TRAC Quarterly Update Fact Sheet"
author: "Will Hopping"
date: "3/10/2022"
output:
  html_notebook:
    df_print: paged
params:
  color_reg: blue
  color_up: green
editor_options:
  chunk_output_type: inline
---
This document provides information on the changes in TRAC output data as we add new partners. <br>
The following data is from data_timestamp = 2022-03-07 <br>
The comparisons between new and old data are filtered to lanes where the aggregation method is zip3-to-zip3 in both new and old data. 
<br><br>


```{r message=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)

# automated script to detect bad records
options(scipen=999)
library(tidyverse)
library(bigrquery)
library(lubridate)
library(ggthemes)
library(DBI)
library(ggplot2)
library(runner)
library(odbc)
library(wesanderson)
library(zoo)
library(logger)
library(jsonlite)
library(stringr)
library(rio)
library(glue)

date_of_data <- "'2022-03-07'"

projectid = "freightwaves-trac-partners-dev"
sql <- glue("SELECT
    data_timestamp,
    rate_type,	
    source,	
    od_pair,	
    comp_key,	
    mode,
    CAST(miles AS FLOAT64) AS miles,
    (CASE
        WHEN miles < 100 THEN '0-100'
        WHEN (miles >= 100 AND miles < 250) THEN '100-250'
        WHEN (miles >= 250 AND miles < 450) THEN '250-450'
        WHEN (miles >= 450 AND miles < 800) THEN '450-800'
        WHEN (miles >= 800 AND miles < 2000) THEN '800-2000' 
        WHEN miles >= 2000 THEN 'greater_than_2000' 
    END) AS mileage_band,
    CAST(effective_miles AS FLOAT64) AS effective_miles,
    CAST(rpm AS FLOAT64) AS rpm,	
    CAST(rpm_low AS FLOAT64) AS rpm_low,	
    CAST(rpm_high AS FLOAT64) AS rpm_high,	
    CAST(rate AS FLOAT64) AS rate,	
    CAST(rate_low AS FLOAT64) AS rate_low,	
    CAST(rate_high AS FLOAT64) AS rate_high,	
    aggregation_method,	
    lane_cities,	
    lane_regions,	
    CAST(lane_confidence_score AS FLOAT64) AS lane_confidence_score,	
    effective_origin_radius,	
    effective_dest_radius,
    effective_time_interval,	
    effective_load_count,	
    total_load_count,	
    CAST(coefficient_of_variation AS FLOAT64) AS coefficient_of_variation,
    CAST(standard_error AS FLOAT64) AS standard_error,	
    generated_on,	
    uuid,	
    aggregation_method_old,	
    CAST(rpm_low_old AS FLOAT64) AS rpm_low_old,	
    CAST(rpm_old AS FLOAT64) AS rpm_old,	
    CAST(rpm_high_old AS FLOAT64) AS rpm_high_old,
    CAST(rate_low_old AS FLOAT64) AS rate_low_old,
    CAST(rate_old AS FLOAT64) AS rate_old,
    CAST(rate_high_old AS FLOAT64) AS rate_high_old,	
    CAST(lane_confidence_score_old AS FLOAT64) AS lane_confidence_score_old,	
    effective_origin_radius_old,	
    effective_dest_radius_old,	
    effective_time_interval_old,	
    CAST(effective_miles_old AS FLOAT64) AS effective_miles_old,	
    effective_load_count_old,	
    total_load_count_old,
    CAST(coefficient_of_variation_old AS FLOAT64) AS coefficient_of_variation_old,
    CAST(standard_error_old AS FLOAT64) AS standard_error_old
FROM `freightwaves-trac-partners-dev.output_daily_rate_data_for_elastic.q1_4new_partners_with_current_prod`
WHERE data_timestamp = {date_of_data}
")

#df1 <- query_exec(sql, projectid, max_pages = Inf, use_legacy_sql = FALSE)
#df1$mileage_band[is.na(df1$mileage_band)] <- 'origin_zip3=dest_zip3'
#write_csv(df1, "Q1_Difference_File_2022-03-07.csv")

# Read in data File
df1 <- read_csv("Q1_Difference_File_2022-03-07.csv")
#Count of total zip3 to zip3 combinations
total_lane_count <- 781456
df2 <- dplyr::filter(df1, aggregation_method == "zip3-to-zip3" & aggregation_method_old == "zip3-to-zip3")
#Color Formatting
colFmt <- function(x,color) {
  ret <- paste("<font color='",color,"'>",x,"</font>",sep="")
  return(ret)
}

```

```{r message=FALSE, warning=FALSE, echo=FALSE}
#-------------> Lane Data Information <-------------#

#1. Aggregation Method Updates
get_agg_method_info <- function(table){
  aggs_new <- table %>%
    group_by(mode, aggregation_method) %>%
    summarise(lanes_new = n())
  aggs_old <- table %>%
    group_by(mode, aggregation_method_old) %>%
    summarise(lanes_old = n())
  colnames(aggs_old)[2] <- 'aggregation_method'
  agg_changes <- dplyr::left_join(aggs_old, aggs_new, by = c('mode'='mode', 'aggregation_method'='aggregation_method'))
  agg_changes1 <- dplyr::mutate(agg_changes, percent_change = ((lanes_new - lanes_old)/lanes_old)*100)
  agg_changes1$percent_change <- paste0(format(round(agg_changes1$percent_change, 1), nsmall = 1), '%')
  return(agg_changes1)
}

aggs <- get_agg_method_info(df1)
van_lanes <- paste0(substr(aggs[8,4], 1, 3), ',', substr(aggs[8,4], 4, 6))
reefer_lanes <- paste0(substr(aggs[4,4], 1, 3), ',', substr(aggs[4,4], 4, 6))
van_change <- paste0(aggs[8,5])
reefer_change <- paste0(aggs[4,5])
van_coverage <- paste0(format(round(((aggs[8,4]/total_lane_count)*100), 1), nsmall = 1), '%')
reefer_coverage <- paste0(format(round(((aggs[4,4]/total_lane_count)*100), 1), nsmall = 1), '%')
```
## Meta Data and Aggregation Method Updates

<br>

#### Zip3-to-zip3 Lanes
**Van** <br>
- Number of Lanes: `r colFmt(van_lanes, params$color_reg)` <br>
- Percent Coverage: `r colFmt(van_coverage, params$color_reg)` <br>
- Percent Increase: `r colFmt(van_change, params$color_up)`

**Reefer** <br>
- Number of Lanes: `r colFmt(reefer_lanes, params$color_reg)`  <br>
- Percent Coverage: `r colFmt(reefer_coverage, params$color_reg)` <br>
- Percent Increase: `r colFmt(reefer_change, params$color_up)` <br>
________________________________________________________________________
<br><br>

```{r message=FALSE, warning=FALSE, echo=FALSE}
#-------------> Total Load Count Information <-------------#

df1V <- dplyr::filter(df1, mode == "Van" & aggregation_method == "zip3-to-zip3" & aggregation_method_old == "zip3-to-zip3")
df1R <- dplyr::filter(df1, mode == "Reefer" & aggregation_method == "zip3-to-zip3" & aggregation_method_old == "zip3-to-zip3")
df1V_1 <- dplyr::select(df1V, od_pair, mode, total_load_count, total_load_count_old)
df1R_1 <- dplyr::select(df1R, od_pair, mode, total_load_count, total_load_count_old)
df1V_2 <- dplyr::mutate(df1V_1, delta = (100*(total_load_count - total_load_count_old)) / total_load_count_old)
df1R_2 <- dplyr::mutate(df1R_1, delta = (100*(total_load_count - total_load_count_old)) / total_load_count_old)
med_incr_loads_V <- median(df1V_2$delta)
med_incr_loads_R <- median(df1R_2$delta)
mil_V <- paste0(format(round(med_incr_loads_V, 1), nsmall = 1), '%')
mil_R <- paste0(format(round(med_incr_loads_R, 1), nsmall = 1), '%')


df2_gathered <- gather(df2, key="dataSet", value = "value", c("total_load_count_old", "total_load_count"))
gg_load_counts <- 
  ggplot(df2_gathered, aes(x=log(value), fill = mode)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~dataSet) +
  geom_vline(xintercept = 7.5, linetype = 'dotted') +
  geom_vline(xintercept = 5, linetype = 'dotted') +
  geom_vline(xintercept = 2.5, linetype = 'dotted')


```
#### Load Counts

**Changes in Load Counts** <br>
Median % increase (Van): `r colFmt(mil_V, params$color_up)` <br>
Median % increase (Reefer): `r colFmt(mil_R, params$color_up)` <br><br>
**Distribution of load counts** <br>
Note that the x-axis is the natural log of the loadcount. 
```{r message=FALSE, warning=FALSE, echo=FALSE}
gg_load_counts
```
________________________________________________________________________
<br>

```{r message=FALSE, warning=FALSE, echo=FALSE}
#-------------> Effective Lookback Information <-------------#

timeV_1 <- dplyr::select(df1V, od_pair, mode, effective_time_interval, effective_time_interval_old)
timeR_1 <- dplyr::select(df1R, od_pair, mode, effective_time_interval, effective_time_interval_old)
timeV_2 <- dplyr::mutate(timeV_1, delta = (effective_time_interval - effective_time_interval_old))
timeR_2 <- dplyr::mutate(timeR_1, delta = (effective_time_interval - effective_time_interval_old))
med_chng_time_V <- median(timeV_2$delta)
med_chng_time_R <- median(timeR_2$delta)
mct_V <- paste0(format(round(med_chng_time_V, 1), nsmall = 1), ' days')
mct_R <- paste0(format(round(med_chng_time_R, 1), nsmall = 1), ' days')

df2_timeframe_gathered <- gather(df2, key="dataSet", value = "value", c("effective_time_interval_old", "effective_time_interval"))
gg_time_frame <- 
  ggplot(df2_timeframe_gathered, aes(x = value, fill = mode)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~dataSet) +
  geom_vline(xintercept = 10, linetype = 'dotted')
  

```

#### Effective Time Frame

**Changes in Effective Timeframe** <br>
Median change (Van): `r colFmt(mct_V, params$color_up)` <br>
Median change (Reefer): `r colFmt(mct_R, params$color_up)` <br><br>
**Distribution of Effective Timeframe**
```{r message=FALSE, warning=FALSE, echo=FALSE}
gg_time_frame
```
________________________________________________________________________
<br>
```{r message=FALSE, warning=FALSE, echo=FALSE}
#-------------> Effective Radius Information <-------------#

radV_1 <- dplyr::select(df1V, od_pair, mode, effective_origin_radius, effective_origin_radius_old, effective_dest_radius, effective_dest_radius_old)
radR_1 <- dplyr::select(df1R, od_pair, mode, effective_origin_radius, effective_origin_radius_old, effective_dest_radius, effective_dest_radius_old)
radV_2 <- dplyr::mutate(radV_1, o_delta = (effective_origin_radius - effective_origin_radius_old))
radR_2 <- dplyr::mutate(radR_1, o_delta = (effective_origin_radius - effective_origin_radius_old))
radV_3 <- dplyr::mutate(radV_2, d_delta = (effective_dest_radius - effective_dest_radius_old))
radR_3 <- dplyr::mutate(radR_2, d_delta = (effective_dest_radius - effective_dest_radius_old))
med_chng_orad_V <- median(radV_3$o_delta)
med_chng_orad_R <- median(radR_3$o_delta)
med_chng_drad_V <- median(radV_3$d_delta)
med_chng_drad_R <- median(radR_3$d_delta)
mco_V <- paste0(format(round(med_chng_orad_V, 2), nsmall = 2), ' miles')
mco_R <- paste0(format(round(med_chng_orad_R, 2), nsmall = 2), ' miles')
mcd_V <- paste0(format(round(med_chng_drad_V, 2), nsmall = 2), ' miles')
mcd_R <- paste0(format(round(med_chng_drad_R, 2), nsmall = 2), ' miles')


df2_radius_gathered <- gather(df2, key="dataSet", value = "value", c("effective_origin_radius_old", "effective_origin_radius", "effective_dest_radius_old", "effective_dest_radius"))

gg_radii <- ggplot(df2_radius_gathered, aes(x = value, fill = mode)) +
            geom_density(alpha = 0.5) +
            facet_wrap(~dataSet) +
            geom_vline(xintercept = 200, linetype = 'dotted')

```
#### Effective Origin/Destination Radius

**Changes in Effective Origin Radius** <br>
Median change (Van): `r colFmt(mco_V, params$color_up)` <br>
Median change (Reefer): `r colFmt(mco_R, params$color_up)` <br><br>
**Changes in Effective Destination Radius** <br>
Median change (Van): `r colFmt(mcd_V, params$color_up)` <br>
Median change (Reefer): `r colFmt(mcd_R, params$color_up)` <br><br>

**Distribution of Effective Origin/Destination Radius** 
```{r message=FALSE, warning=FALSE, echo=FALSE}
gg_radii
```
________________________________________________________________________
<br>

```{r message=FALSE, warning=FALSE, echo=FALSE}
#-------------> Coefficient of Variation and Standard Error Information <-------------#

coef_var <- gather(df2, key="dataSet", value = "value", c("coefficient_of_variation_old", "coefficient_of_variation"))
gg_coef_var <- 
  ggplot(coef_var, aes(x = value, fill = mode)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~dataSet) +
  geom_vline(xintercept = 0.13, linetype = 'longdash') +
  geom_vline(xintercept = 0.17, linetype = 'longdash') +
  xlim(0,0.4)

st_error <- gather(df2, key="dataSet", value = "value", c("standard_error_old", "standard_error"))
gg_st_error <- 
  ggplot(st_error, aes(x = value, fill = mode)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~dataSet) +
  geom_vline(xintercept = 0.05, linetype = 'longdash') +
  xlim(0,0.25)

```
#### Coefficient of Variation and Standard Error


**Distribution of Coefficient of Variation**<br>
```{r message=FALSE, warning=FALSE, echo=FALSE}
gg_coef_var
```
<br>
**Distribution of Standard Error**<br>
```{r message=FALSE, warning=FALSE, echo=FALSE}
gg_st_error
```
________________________________________________________________________
<br>
```{r message=FALSE, warning=FALSE, echo=FALSE}
#-------------> Confidence Score Information <-------------#

csV <- dplyr::select(df1V, od_pair, mode, lane_confidence_score, lane_confidence_score_old)
csR <- dplyr::select(df1R, od_pair, mode, lane_confidence_score, lane_confidence_score_old)
csV_2 <- dplyr::mutate(csV, delta = (lane_confidence_score - lane_confidence_score_old))
csR_2 <- dplyr::mutate(csR, delta = (lane_confidence_score - lane_confidence_score_old))
med_chng_cs_V <- mean(csV_2$delta)
med_chng_cs_R <- mean(csR_2$delta)

cs1 <- dplyr::select(df2, od_pair, mode, lane_confidence_score, lane_confidence_score_old)
cs2 <- cs1 %>%
  group_by(mode, lane_confidence_score) %>%
  summarise(counts_new = n())
cs3 <- cs1 %>%
  group_by(mode, lane_confidence_score_old) %>%
  summarise(counts_old = n())
cs4 <- dplyr::left_join(cs2, cs3, by = c("mode"="mode", "lane_confidence_score"="lane_confidence_score_old"))


```
#### Confidence Score distributions, New vs Old

**Note:** The confidence scores for the new data use a different calculation method than the scores for the old data and are not comparable. This is simply to illustrate how they will change when the new method goes into effect. <br>
`r cs4`<br>

```{r message=FALSE, warning=FALSE, echo=FALSE}
#-------------> Overall Rate Data Information <-------------#

# 1. changes in rate info
get_rpm_changes <- function(table){
  df2 <- dplyr::filter(table, aggregation_method == 'zip3-to-zip3' & aggregation_method_old == 'zip3-to-zip3')
  rpm_1 <- dplyr::select(df2, od_pair, mode, mileage_band, rpm, rpm_old)
  rpm_2 <- dplyr::mutate(rpm_1, delta = rpm - rpm_old)
  rpm_3 <- dplyr::mutate(rpm_2, pct_diff = ((rpm-rpm_old)/rpm_old))
  return(rpm_3)
}

rpm <- get_rpm_changes(df1)
rpm_less_250 <- dplyr::filter(rpm, mileage_band %in% c('0-100', '100-250', 'origin_zip3=dest_zip3'))
rpm_greater_250 <- dplyr::filter(rpm, mileage_band %in% c('250-450', '450-800', '800-2000', 'greater_than_2000'))

get_actual_rpm_change <- function(table){
  actual_change <- table %>%
  group_by(mode, mileage_band) %>%
  summarise(lane_count = n(), median_absolute_change = median(abs(delta)), average_absolute_change = mean(abs(delta)), median_change = median(delta),
            avg_change = mean(delta))
  actual_change$median_absolute_change <- format(round(actual_change$median_absolute_change, 2), nsmall = 2)
  actual_change$average_absolute_change <- format(round(actual_change$average_absolute_change, 2), nsmall = 2)
  actual_change$median_change <- format(round(actual_change$median_change, 2), nsmall = 2)
  actual_change$avg_change <- format(round(actual_change$avg_change, 2), nsmall = 2)
  return(actual_change)
}


get_pct_rpm_change <- function(table){
  actual_change <- table %>%
    group_by(mode, mileage_band) %>%
    summarise(lane_count = n(), median_absolute_change = median(abs(pct_diff)), average_absolute_change = mean(abs(pct_diff)), median_change =
                median(pct_diff), avg_change = mean(pct_diff))
  actual_change$median_absolute_change <- paste0(format(round(actual_change$median_absolute_change*100, 2), nsmall = 2), '%')
  actual_change$average_absolute_change <- paste0(format(round(actual_change$average_absolute_change*100, 2), nsmall = 2), '%')
  actual_change$median_change <- paste0(format(round(actual_change$median_change*100, 2), nsmall = 2), '%')
  actual_change$avg_change <- paste0(format(round(actual_change$avg_change*100, 2), nsmall = 2), '%')
  return(actual_change)
}
  
actual_change_all_lanes <- get_actual_rpm_change(rpm)
pct_change_all_lanes <- get_pct_rpm_change(rpm)

gg_pct_under_250 <- ggplot(rpm_less_250, aes(x=mileage_band, y=pct_diff, fill=mode)) +
  geom_violin() +
  ggtitle("Percent Change in RPM for Shipments Less Than 250 Miles") +
  ylab("Percent Change") +
  xlab("Mileage Band") +
  ylim(-.5, .75)

gg_pct_over_250 <- ggplot(rpm_greater_250, aes(x=mileage_band, y=pct_diff, fill=mode)) +
  geom_violin() +
  ggtitle("Percent Change in RPM for Shipments Greater Than 250 Miles") +
  ylab("Percent Change") +
  xlab("Mileage Band") +
  ylim(-.25, .25)

gg_delta_under_250 <- ggplot(rpm_less_250, aes(x=mileage_band, y=delta, fill=mode)) +
  geom_violin() +
  ggtitle("Difference Between New and Old RPMs for Shipments Less Than 250 Miles") +
  ylab("Delta RPM (New minus Old)") +
  xlab("Mileage Band") +
  ylim(-2.5, 7.5)

gg_delta_over_250 <- ggplot(rpm_greater_250, aes(x=mileage_band, y=delta, fill=mode)) +
  geom_violin() +
  ggtitle("Difference Between New and Old RPMs for Shipments Greater Than 250 Miles") +
  ylab("Delta RPM (New minus Old)") +
  xlab("Mileage Band") +
  ylim(-1, 1) 

```

## RPM Changes: All Lanes

Actual change in rpm by mode and mileage band (in Dollars) <br>
`r actual_change_all_lanes`<br>
Percent change in rpm by mode and mileage band <br>
`r pct_change_all_lanes`
<br><br>

**Note:** The upper and lower bounds of the y-axes in the violin plots below have been manually set. There are further outliers not being displayed, but those outliers account for a very small portion of the data. <br>
```{r eval=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
gg_pct_under_250
gg_pct_over_250
gg_delta_under_250
gg_delta_over_250
```
<br><br>

```{r message=FALSE, warning=FALSE, echo=FALSE}
#-------------> High/Low Spread Information <-------------#

highlowV_1 <- dplyr::select(df1V, od_pair, mode, rpm_high, rpm_low, rpm_high_old, rpm_low_old)
highlowR_1 <- dplyr::select(df1R, od_pair, mode, rpm_high, rpm_low, rpm_high_old, rpm_low_old)
highlowV_2 <- dplyr::mutate(highlowV_1, delta_old = (rpm_high_old - rpm_low_old))
highlowR_2 <- dplyr::mutate(highlowR_1, delta_old = (rpm_high_old - rpm_low_old))
highlowV_3 <- dplyr::mutate(highlowV_2, delta_new = (rpm_high - rpm_low))
highlowR_3 <- dplyr::mutate(highlowR_2, delta_new = (rpm_high - rpm_low))
med_highlow_old_V <- paste0("$",format(round(median(highlowV_3$delta_old), 2), nsmall = 2))
med_highlow_old_R <- paste0("$",format(round(median(highlowR_3$delta_old), 2), nsmall = 2))
med_highlow_new_V <- paste0("$",format(round(median(highlowV_3$delta_new), 2), nsmall = 2))
med_highlow_new_R <- paste0("$",format(round(median(highlowR_3$delta_new), 2), nsmall = 2))


highlow_delta1 <- dplyr::mutate(df2, delta_old = (rpm_high_old - rpm_low_old))
highlow_delta2 <- dplyr::mutate(highlow_delta1, delta_new = (rpm_high - rpm_low))
highlow_delta_gathered <- gather(highlow_delta2, key="dataSet", value = "value", c("delta_new", "delta_old"))
gg_highlow <- 
  ggplot(highlow_delta_gathered, aes(x = value, fill = mode)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~dataSet) +
  geom_vline(xintercept = 0.5, linetype = 'dotted') +
  xlim(0,2)
  

```
#### Change in spread between High and Low RPMs

**Difference Between rpm_high and rpm_low (Van)** <br>
Median difference (Old): `r colFmt(med_highlow_old_V, params$color_up)` <br>
Median difference (New): `r colFmt(med_highlow_new_V, params$color_up)` <br><br>
**Difference Between rpm_high and rpm_low (Reefer)** <br>
Median difference (Old): `r colFmt(med_highlow_old_R, params$color_up)` <br>
Median difference (New): `r colFmt(med_highlow_new_R, params$color_up)` <br><br>

**Distribution of Deltas (rpm_high - rpm_low)** 
```{r message=FALSE, warning=FALSE, echo=FALSE}
gg_highlow
```
<br><br>
```{r message=FALSE, warning=FALSE, echo=FALSE}
#-------------> Rate Data Information Top Volume Lanes <-------------#

get_intersect_top_x_pct <- function(table, eq_type, pct_as_decimal){
  basic1 <- dplyr::filter(table, aggregation_method == 'zip3-to-zip3' & aggregation_method_old == 'zip3-to-zip3')
  basic2 <- dplyr::select(basic1, comp_key, od_pair, mode, total_load_count, total_load_count_old)
  old_van <- basic2 %>%
    select(comp_key, od_pair, mode, total_load_count_old) %>%
    filter(mode == eq_type) %>%
    arrange(desc(total_load_count_old))
  old_van_t100 <- old_van[1:(ceiling(pct_as_decimal*length(old_van$comp_key))),]
  new_van <- basic2 %>%
    select(comp_key, od_pair, mode, total_load_count) %>%
    filter(mode == eq_type) %>%
    arrange(desc(total_load_count))
  new_van_t100 <- new_van[1:(ceiling(pct_as_decimal*length(new_van$comp_key))),]
  van_t100 <- dplyr::inner_join(old_van_t100, new_van_t100, by = c('od_pair'='od_pair', 'mode'='mode', 'comp_key'='comp_key'))
  return(van_t100$comp_key)
}

top10pct_van <- get_intersect_top_x_pct(df1, 'Van', 0.1)
top10pct_reefer <- get_intersect_top_x_pct(df1, 'Reefer', 0.1)
top10_combined <- c(top10pct_van, top10pct_reefer)
top10_df <- dplyr::filter(df1, comp_key %in% top10_combined)
top10_df1 <- get_rpm_changes(top10_df)
actual_change_10_lanes <- get_actual_rpm_change(top10_df1)
pct_change_10_lanes <- get_pct_rpm_change(top10_df1)


gg_top10_pct <- ggplot(top10_df1, aes(x=mileage_band, y=pct_diff, fill=mode)) +
  geom_violin() +
  ggtitle("Percent Change in RPM for Top 10% of Lanes by Volume") +
  ylab("Percent Change") +
  xlab("Mileage Band") +
  ylim(-0.1, 0.25)

gg_top10_delta <- ggplot(top10_df1, aes(x=mileage_band, y=delta, fill=mode)) +
  geom_violin() +
  ggtitle("Difference Between New and Old RPMs for Top 10% of Lanes by Volume") +
  ylab("Delta RPM (New minus Old)") +
  xlab("Mileage Band") +
  ylim(-0.5, 1.25)

```

## RPM Changes: Top 10% of Lanes by Volume 

**Note:** The top 10% of lanes by volume only exist in the mileage bands 250-450, 450-800, and 800-2000. <br>

Actual change in rpm by mode and mileage band (in Dollars) <br>
`r actual_change_10_lanes`<br>
Percent change in rpm by mode and mileage band <br>
`r pct_change_10_lanes`
<br><br>
**Note:** The upper and lower bounds of the y-axes in the violin plots below have been manually set. There are further outliers not being displayed, but those outliers account for a very small portion of the data. <br>
```{r eval=TRUE, message=FALSE, warning=FALSE, echo=FALSE}
gg_top10_pct
gg_top10_delta
```


